QPLIB: A Library of Quadratic Programming Instances

### 2017-01-30 QPLIB-2.2.tex
emphasize early that optimization sense can be maximization
fixes to bibliography
- remove duplicates, update references, etc

We will now provide a first general discussion about the different problem classes that our proposed taxonomy defines. Some of them are actually ``too simple'' to make sense in our context. For instance, D*B problems have only diagonal quadratic (hence separable) objective function and bound constraints; as such, they read
\[
 \textstyle
 \min \; \Big\{ \,
 \sum_{j \in \Mcn} \big( \, Q^0_j x_j^2 + b^0_j x_j \, \big) \;:\;
 l_j \leq x_j \leq u_j \quad j \in \Mcn \;\;,\;\;
 x_j \in \mathbb{Z} \quad j \in \Mcz \, \Big\}
 \;\; .
\]
Hence, their solution only requires the independent minimization of a convex quadratic univariate function in each single variable $x_j$ over a box constraint and possibly integrality requirements, which can be attained trivially in $O(1)$ (per variable) by closed-form formul{\ae}, projection and rounding arguments. \emph{A fortiori}, the even simpler cases L*B, D*N and L*N (the latter obviously unbounded unless $b^0 = 0$) will not be discussed here. Similarly, CCN are immediately solved by linear algebra techniques, and therefore are of no interest in this context. On the other end of the spectrum, in general QP is a hard problem. Actually, LIQ---linear objective function and quadratic constraints in integer variables with no finite bounds, i.e. 
\[
 \textstyle
 \min \; \Big\{ \, b^0 x \;:\;
 x^\top Q^i x + b^i x \leq c^i \quad i \in \Mcm \;\;,\;\;
 x_j \in \mathbb{Z} \quad j \in \Mcn \, \Big\}
 \;\; ,
\]
is not only $\mathcal{NP}$-hard, but downright undecidable \cite{jeroslow}. Hence so are the ``harder'' \{C,Q\}IQ.

@@

 \item \emph{Nonconvex Continuous Quadratic Programs} QCQ are instead in general $\mathcal{NP}$-hard, even if the constraints are very specific (QCB) and only one eigenvalue of $Q^0$ is negative \cite{Hemmecke2010}. They therefore require enumerative techniques like the spatial Branch\&Bound \cite{FV90,BLLMW09}, to be solved to optimality. Of course, local approaches are available that are able to efficiently provide saddle points (hopefully, local optima) of the CQC, but providing global guarantees about the quality of the obtained solutions is challenging. In our library we have specifically focussed on  \emph{exact} solution of the instances.

>>>>

We will now provide a first general discussion about the different problem classes that our proposed taxonomy defines.
For simplicity, we will assume minimization problems for the remaining of this section.
Some problem classes are actually ``too simple'' to make sense in our context. For instance, D*B problems have only diagonal quadratic (hence separable) objective function and bound constraints; as such, they read
\[
 \textstyle
 \min \; \Big\{ \,
 \sum_{j \in \Mcn} \big( \, Q^0_j x_j^2 + b^0_j x_j \, \big) \;:\;
 l_j \leq x_j \leq u_j \quad j \in \Mcn \;\;,\;\;
 x_j \in \mathbb{Z} \quad j \in \Mcz \, \Big\}
 \;\; .
\]
Hence, their solution only requires the independent minimization of a convex quadratic univariate function in each single variable $x_j$ over a box constraint and possibly integrality requirements, which can be attained trivially in $O(1)$ (per variable) by closed-form formul{\ae}, projection and rounding arguments. \emph{A fortiori}, the even simpler cases L*B, D*N and L*N (the latter obviously unbounded unless $b^0 = 0$) will not be discussed here. Similarly, CCN are immediately solved by linear algebra techniques, and therefore are of no interest in this context. On the other end of the spectrum, in general QP is a hard problem. Actually, LIQ---linear objective function and quadratic constraints in integer variables with no finite bounds, i.e. 
\[
 \textstyle
 \min \; \Big\{ \, b^0 x \;:\;
 x^\top Q^i x + b^i x \leq c^i \quad i \in \Mcm \;\;,\;\;
 x_j \in \mathbb{Z} \quad j \in \Mcn \, \Big\}
 \;\; ,
\]
is not only $\mathcal{NP}$-hard, but downright undecidable \cite{jeroslow}. Hence so are the ``harder'' \{C,Q\}IQ.

@@

 \item \emph{Nonconvex Continuous Quadratic Programs} QCQ are instead in general $\mathcal{NP}$-hard, even if the constraints are very specific (QCB) and only one eigenvalue of $Q^0$ is negative \cite{Hemmecke2010}. They therefore require enumerative techniques like the spatial Branch\&Bound \cite{FV90,BeLeLiMaWa08}, to be solved to optimality. Of course, local approaches are available that are able to efficiently provide saddle points (hopefully, local optima) of the CQC, but providing global guarantees about the quality of the obtained solutions is challenging. In our library we have specifically focussed on  \emph{exact} solution of the instances.
